An excess of positive results: Comparing the standard Psychology literature with Registered Reports

### 2020-02-05 preprint/positive_results_SRs_RRs.tex
added link to dataset

Data and code necessary to reproduce all analyses reported here, as well as the \href{https://osf.io/qw798/}{Appendix}, the \href{https://osf.io/sy927/}{preregistration}, and additional supplementary files, are available at \url{https://osf.io/dbhgr}. The manuscript including figures and statistical analyses, the \href{https://osf.io/qw798/}{Appendix}, and the \href{https://osf.io/6jrkz/}{codebook} available in the supplement were created using RStudio (1.2.5019, RStudio Team, 2019) and R (Version 3.6.0; R Core Team, 2019) and the R-packages \emph{bookdown} (Version 0.17; Xie, 2016), \emph{codebook} (Version 0.8.2; Arslan, 2018), \emph{ggplot2} (Version 3.1.1; Wickham, 2016), \emph{here} (Version 0.1; Müller, 2017), \emph{knitr} (Version 1.26; Xie, 2015), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{reshape2} (Version 1.4.3; Wickham, 2007), \emph{rio} (Version 0.5.16; Chan, Chan, Leeper, \& Becker, 2018), \emph{rmarkdown} (Version 1.18; Xie, Allaire, \& Grolemund, 2018), \emph{stringr} (Version 1.4.0; Wickham, 2019), and \emph{TOSTER} (Version 0.3.4; Lakens, 2017).

>>>>

\href{https://osf.io/aqr2s/}{Data} and code necessary to reproduce all analyses reported here, as well as the \href{https://osf.io/qw798/}{Appendix}, the \href{https://osf.io/sy927/}{preregistration}, and additional supplementary files, are available at \url{https://osf.io/dbhgr}. The manuscript, including figures and statistical analyses, the \href{https://osf.io/qw798/}{Appendix}, and the \href{https://osf.io/6jrkz/}{codebook} available in the supplement were created using RStudio (1.2.5019, RStudio Team, 2019) and R (Version 3.6.0; R Core Team, 2019) and the R-packages \emph{bookdown} (Version 0.17; Xie, 2016), \emph{codebook} (Version 0.8.2; Arslan, 2018), \emph{ggplot2} (Version 3.1.1; Wickham, 2016), \emph{here} (Version 0.1; Müller, 2017), \emph{knitr} (Version 1.26; Xie, 2015), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{reshape2} (Version 1.4.3; Wickham, 2007), \emph{rio} (Version 0.5.16; Chan, Chan, Leeper, \& Becker, 2018), \emph{rmarkdown} (Version 1.18; Xie, Allaire, \& Grolemund, 2018), \emph{stringr} (Version 1.4.0; Wickham, 2019), and \emph{TOSTER} (Version 0.3.4; Lakens, 2017).
